Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-13 RR_manuscript/Draft_RR.Rmd
♻️ - edit between-teams variability section

msa_sd_sd_lo <- msa_sd %>%
  mutate(
    across(starts_with("sd_"), ~.x * meta_sd_clo),
    ci = "low"
  ) %>%
  pivot_longer(sd_min:sd_max, names_to = "sd")
msa_sd_sd_hi <- msa_sd %>%
  mutate(
    across(starts_with("sd_"), ~.x * meta_sd_chi),
    ci = "high"
  ) %>%
  pivot_longer(sd_min:sd_max, names_to = "sd")

msa_sd_sd <- bind_rows(msa_sd_sd_lo, msa_sd_sd_hi)
```

@@

We illustrate what all this means in actual acoustic measures by means of examples, taking the minimum and maximum sample standard deviation of each measure from our data.

@@

<!-- TR: cannot really talk about tiny effects because we have the continuous typicality included and that looks at a difference of one unit (which is 1 in a 1-100 scale -->

>>>>

msa_sd_sd_lo <- msa_sd %>%
  mutate(
    across(starts_with("sd_"), ~.x * meta_sd_clo * 1.96),
    ci = "low"
  ) %>%
  pivot_longer(sd_min:sd_max, names_to = "sd")
msa_sd_sd_hi <- msa_sd %>%
  mutate(
    across(starts_with("sd_"), ~.x * meta_sd_chi * 1.96),
    ci = "high"
  ) %>%
  pivot_longer(sd_min:sd_max, names_to = "sd")

msa_sd_sd <- bind_rows(msa_sd_sd_lo, msa_sd_sd_hi) %>%
  mutate(value = round(value, 1)) %>%
  pivot_wider(names_from = c(ci, sd), values_from = value) %>%
  unite("low", low_sd_min, low_sd_max, sep = "-") %>%
  unite("high", high_sd_min, high_sd_max, sep = "-") %>%
  mutate(
    unit = c("ms", "ms", "hz", "hz", "dB", "dB")
  )
```

@@

```{r}
knitr::kable(msa_sd, digits = 1)
```

We illustrate what this means in actual acoustic measures by means of examples.
For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
We then selected representative values of standard deviations for the three outcome measurements extracted either from specific segments or words.

Table XXX reports the minimum and maximum SD values taken from a representative range.
If we take segments, we have found duration measurements (as taken by the teams who used duration) to have standard deviations that range between 33.4 and 51.4 ms.
Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between `r round(meta_bm_tidy$conf.low[["sd_model_id__Intercept"]], 2)` and `r round(meta_bm_tidy$conf.high[["sd_model_id__Intercept"]], 2)`, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: $33.4 * 0.11 = 3.8$ ms, $51.4 * 0.11 = 5.7$ ms;  $33.4 * 0.15 = 5$ ms, $51.4 * 0.15 = 7.7$ ms.
We can thus calculate 95% intervals of the estimated between-model variability in milliseconds: `r round(3.8*1.96, 1)`-`r round(5.7*1.96, 1)` ms based on the low CI estimate 0.11, `r round(5*1.96, 1)`-`r round(7.7*1.96, 1)` ms based on the high CI estimate 0.15.

```{r}
msa_sd_sd
```

@@

### 2022-09-13 RR_manuscript/Draft_RR.tex
♻️ - edit RR; include new shrinkage plot
♻️ - edit between-teams variability section

We illustrate what all this means in actual acoustic measures by means of examples, taking the minimum and maximum sample standard deviation of each measure from our data.

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figs/meta_plot1_nest} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
\end{figure}

>>>>

\begin{tabular}{l|l|r|r}
\hline
outcome & temporal\_window & sd\_min & sd\_max\\
\hline
duration & segment & 33.4 & 51.4\\
\hline
duration & word & 32.6 & 119.8\\
\hline
f0 & segment & 40.2 & 44.6\\
\hline
f0 & word & 4.0 & 47.2\\
\hline
intensity & segment & 3.3 & 7.1\\
\hline
intensity & word & 3.5 & 3.9\\
\hline
\end{tabular}

We illustrate what this means in actual acoustic measures by means of examples.
For each of the submitted analyses that included duration, fundamental frequency or intensity as outcome, we have calculated the standard deviation of those measures in the submitted data table.
We then selected representative values of standard deviations for the three outcome measurements extracted either from specific segments or words.

Table XXX reports the minimum and maximum SD values taken from a representative range.
If we take segments, we have found duration measurements (as taken by the teams who used duration) to have standard deviations that range between 33.4 and 51.4 ms.
Given that the estimated between-model variability in standard units as we obtained from the meta-analytic estimate is between 0.11 and 0.15, we can convert the standard units into milliseconds by multiplying them with the standard deviation values in milliseconds: \(33.4 * 0.11 = 3.8\) ms, \(51.4 * 0.11 = 5.7\) ms; \(33.4 * 0.15 = 5\) ms, \(51.4 * 0.15 = 7.7\) ms.
We can thus calculate 95\% intervals of the estimated between-model variability in milliseconds: 7.4-11.2 ms based on the low CI estimate 0.11, 9.8-15.1 ms based on the high CI estimate 0.15.

\begin{verbatim}
## # A tibble: 6 x 5
##   outcome   temporal_window low      high     unit 
##   <chr>     <chr>           <chr>    <chr>    <chr>
## 1 duration  segment         7.4-11.4 10-15.4  ms   
## 2 duration  word            7.2-26.5 9.8-35.8 ms   
## 3 f0        segment         8.9-9.8  12-13.3  hz   
## 4 f0        word            0.9-10.4 1.2-14.1 hz   
## 5 intensity segment         0.7-1.6  1-2.1    dB   
## 6 intensity word            0.8-0.9  1-1.2    dB
\end{verbatim}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figs/meta_plot1_shrinkage} \caption{(ref:metaPlot1)}\label{fig:plot-meta1}
\end{figure}
